Statistical Inference for inter-arrival times of extreme events in bursty time series

### 2018-12-09 article_springer/article_springer.Rmd
fix one square bracket

Figure \ref{fig:flares} shows the stability plots for the solar flare data, on the left for the tail parameter and on the right for the scale parameter. Dotted lines show 95% confidence intervals, which are derived from the asymptotic normality of the log-moments estimators [@Cahoy2013] and the $\delta$-method [@MittagLeffleR, dashed lines show the actual values of $\beta$ resp.\ $\sigma_0$. The stability plot for the tail stabilizes nicely round about 0.85 (dotted line), while it is a little bit harder to deduce an estimate for the scale parameter. Howerever, the stability plot for the scale parameter seems to stabilize round about $3 \times 10^7$.

>>>>

Figure \ref{fig:flares} shows the stability plots for the solar flare data, on the 
left for the tail parameter and on the right for the scale parameter. Dotted lines 
show 95% confidence intervals, which are derived from the asymptotic normality of 
the log-moments estimators [@Cahoy2013] and the $\delta$-method 
[see @MittagLeffleR], 
dashed lines show the actual values of $\beta$ resp.\ $\sigma_0$. The stability 
plot for the tail stabilizes nicely round about 0.85 (dotted line), while it is a 
little bit harder to deduce an estimate for the scale parameter. Howerever, the 
stability plot for the scale parameter seems to stabilize round about $3 \times 
10^7$.
